---
title: "esm206 Lab 8"
author: "Sarah Lam"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelsummary)
library(broom)
library(here)
library(corrplot)
```

### Read in slo_homes.csv data 

```{r}
homes <- read_csv(here("data", "slo_homes.csv"))

#use unique(homes$City) to check cities in dataframe 
```

### Create a subset with 4 cities 

Tasl: createa a seubset called homes_subset) that only contains observations where the city is: 

- "San Luis Obispo"
_ "Atascadero" 
- "Arroyo Grange" 
- "Santa Maria-Orcutt" 
 
```{r}
homes_subset <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt"))
```
 
### A little exploration 

Task: Create a summary table that has the mean an standard deviation of hom eprices grouped by city and sale status 

```{r, include = FALSE, eval = FALSE}
#eval = FALSE means that the code doesn't run at all, can be useful for exploratory summary statistics on really big datasets 
home_summary <- homes_subset %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price, na.rm = TRUE),
            sd_price = sd(Price, na.rm = TRUE))
```

Task: explore the relationship between square footage and home price (from homes_subset) in a scatterplot. 

```{r}
ggplot(data = homes_subset, aes(x = SqFt, y = Price)) +
  geom_point(aes(color = City)) +
  scale_y_continuous(breaks = c(0, 2000000, 4000000),
                     labels = c('0', '2,000,000', '4,000,000')) +
  theme_minimal() +
  geom_smooth(method = "lm")
```

### Try a few linear models 

Use multiple linear regression to investigate relationships between several predictor variables and home Price, using homes_subset. 

Create 2 different permutations of this model: 

(1) Price ~ City, Bedrooms, Bathrooms, SqFt, Status
(2) Price ~ City, SqFt, Status(lm2)
(3) Try another one (lm3)

```{r}
lm1 <- lm(data = homes_subset, Price ~ City + Bedrooms + Bathrooms + SqFt + Status)
# R^2 = 54% this means that 54% of variance in home price is explained by variables in this model 

lm2 <- lm(data = homes_subset, Price ~ City +SqFt +Status) 

lm3 <- lm(data = homes_subset, Price ~ SqFt)

# If I wanted San Luis Obispo to be the reference level: 
#Use fct_relevel() to specify a new reference level 

new_homes_subset <- homes_subset %>% 
  mutate(City = fct_relevel(City, "San Luis Obispo"))
```

### Explore correlations between quantitative variables 

Task: make a subset called homes_quant (starting from homes_subset) that only contains the variables from Price through SqFt). 

```{r}
homes_quant <- homes_subset %>% 
  select(Price:SqFt)

homes_cor <- cor(homes_quant)

corrplot(homes_cor, method = "ellipse")
```

### Compare AIC values

```{r}
AIC(lm1)
AIC(lm2)
```

### Use modelsummary() to return multiple model outputs 

```{r}
modelsummary(list(lm1, lm2, lm3))
```

### Use broom::augment() to return the predictions for existing bservaions 

```{r}
home_predictions <- augment(lm1)

#Make a histogram of the residuals from this model (lm1)

ggplot(data = home_predictions, aes(x = .resid)) +
  geom_histogram()
```

# BRANCH TEST TEST TEST TEST TEST TEST TEST




